---
title: "simple math for binomial distributions"
author: "Thomas Hoversen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial distribution}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial Distribution

Say you have three inputs: success, trials, and prob. The following tutorial will show you how to calculate the binomial distribution of those inputs, then put them into a nice table.

binomial distribution:

```{r}
hearts <- bin_probability(success = 3, trials = 9, prob = 0.33)
hearts
```

a nice table format:

```{r}
diamonds <- bin_distribution(trials = 9, prob = 0.33)
diamonds
```

Say you want to take this table and add another column that adds the cumulative sum of the probability distribution. 

The function to do that is:

```{r}
clubs <- bin_cumulative(trials = 9, prob = 0.33)
```

May be you decide this information is good but you want a little more detail. If this is the case you can get a summary in an object of class "binvar", complete with a list with named elements. You can get just the most basic trial and probability variables, or you can call a more detailed output that includes the mean, mode, variance, skewness, and kurtosis of the probability distribution.

If you just want the basic trial and probability variables:

```{r}
spades <- bin_variable(30, 0.7)
spades
```

For a more detailed output:

```{r}
ace <- bin_variable(trials = 10, p = 0.3)
cards <- summary(ace)
cards
```

When you are ready to graph, you'll have two options to do this. You can invoke 'plot.bindis()' to graph just the binomial distribution. 

The following code graphs the binomial distribution automatically as a bar graph:

```{r}
plot.bindis(trials = 5, prob = 0.5)
```

Finally, if you create an object that stores the output of a table with a cumulative binomial distribution, you can invoke 'plit.bincum()' to graph the cumulative binomial distribution.

The following code graphs the cumulative binomial distribution automatically as a line graph:

```{r}
plot.bincum(trials = 5, prob = 0.5)
```


# Conclusion

This package is perfect for basic binomial distribution problems and can be incorporated into any coding routine in a fluid and seemless manor. 











